Effort and Delay Discounting in a Foraging Environment

### 2019-05-07 Cost2/Cost2_prereg_remake.Rmd
overall prop section complete

## Functions
# Permutation for 2 groups
permute <- function(group1 = 1, group2 = 2, statType = mean, nPerms = 5000, paired = FALSE){

@@

@@

``` {r 16.2.1. Overall Proportion/Earnings,fig.align="center",fig.width=10,fig.height=4, echo=FALSE}  
## prop complete
# ecdfs
wait <- ecdf(summaryData$propComplete[indxWait])
cog <- ecdf(summaryData$propComplete[indxCog])
phys <- ecdf(summaryData$propComplete[indxPhys])
easy <- ecdf(summaryData$propComplete[indxEasy])
range <- seq(0,1,by=0.01)

test <- data.frame(range = range,
                   ecdf = c(wait(range),cog(range),phys(range),easy(range)),
                   Group = factor(c(rep("Wait",101),rep("Cognitive",101),rep("Physical",101),rep("Easy", 101)), levels = c("Wait","Cognitive","Physical","Easy")))

p1 <- ggplot(test, aes(x=range,y=ecdf, group=Group, color=Group))
p1 <- p1 + geom_line(show.legend = F, size = 1.5) +
    scale_color_manual(values = cols) +
    labs(title = "ECDF of Acceptances per Group", y="ECDF", x = "Proportion Accepted") +
    theme_classic()

# problem is, data is not normal, so we're going to bootstrap it and DEFINITELY permute
# Bootstrap nonparametric
B <- 5000
meanBootW <- bootstrap(summaryData$propComplete[indxWait],B = B) #rep(0,B)
meanBootC <- bootstrap(summaryData$propComplete[indxCog], B = B) #rep(0,B)
meanBootP <- bootstrap(summaryData$propComplete[indxPhys], B = B)
meanBootE <- bootstrap(summaryData$propComplete[indxEasy], B = B)

#CIs wait
meanW <- mean(meanBootW)
upperW <- quantile(meanBootW,0.975) # meanBoot?
lowerW <- quantile(meanBootW,0.025)

#CIs effort
meanC <- mean(meanBootC)
upperC <- quantile(meanBootC,0.975) # meanBoot?
lowerC <- quantile(meanBootC,0.025)

#CIs physical
meanP <- mean(meanBootP)
upperP <- quantile(meanBootP,0.975) # meanBoot?
lowerP <- quantile(meanBootP,0.025)

#CIs easy
meanE <- mean(meanBootE)
upperE <- quantile(meanBootE,0.975) # meanBoot?
lowerE <- quantile(meanBootE,0.025)

# formal testing 
# proportion completed
propAov <- aov(propComplete ~ factor(Group), data = summaryData)

# effect size (get the one for anovas)
# propRsq <- cohenD(summaryData$propComplete[indxWait],summaryData$propComplete[indxCog])

# post-hoc
temp <- do.call(cbind, lapply(split(summaryData, summaryData$Group),"[[","propComplete"))
temp2 <- t(combn(colnames(temp),2))

propTests <- data.frame(Comparison = paste(temp2[,1], temp2[,2]),
                        T_pval = rep(1,6),
                        CohenD = rep(0,6))

for (i in seq(nrow(temp2))) {

  propTests$T_pval[i] <- round(permute(temp[,temp2[i,1]], temp[,temp2[i,2]])$Pval, digits = 2)
  propTests$CohenD[i] <- round(cohenD(temp[,temp2[i,1]], temp[,temp2[i,2]]), digits = 2)

# earnings
earnAov <- aov(Earnings ~ factor(Group), data = summaryData)

# effect size
# earnRsq <- cohenD(summaryData$propComplete[indxWait],summaryData$propComplete[indxCog])

# post-hoc
temp <- do.call(cbind, lapply(split(summaryData, summaryData$Group),"[[","Earnings"))
temp2 <- t(combn(colnames(temp),2))

earnTests <- data.frame(Comparison = paste(temp2[,1], temp2[,2]),
                        T_pval = rep(1,6),
                        CohenD = rep(0,6))

for (i in seq(nrow(temp2))) {

  earnTests$T_pval[i] <- round(permute(temp[,temp2[i,1]], temp[,temp2[i,2]])$Pval, digits = 2)
  earnTests$CohenD[i] <- round(cohenD(temp[,temp2[i,1]], temp[,temp2[i,2]]), digits = 2)

rm(B,cog,wait,phys,easytemp,temp2)

# plot
p2 <- ggplot(summaryData, aes(x=Group, y=propComplete, fill = Group))
p2 <- p2 + geom_boxplot(show.legend = F) +
    scale_fill_manual(values = cols) +
    ylim(c(0,1)) +
    labs(title = "Proportion Completed by Group", y="Proportion Completed") +
    theme_classic()

p3 <- ggplot(summaryData, aes(x=Group, y=Earnings, fill = Group))
p3 <- p3 + geom_boxplot(show.legend = F) +
    scale_fill_manual(values = cols) +
    labs(title = "Earnings by Group", y="Total Earnings (Cents)") +
    theme_classic()

>>>>

## Functions
# Permutation for 2 groups
permute <- function(group1 = 1, group2 = 2, statType = mean, nPerms = 5000, paired = FALSE, simple = FALSE){

@@

    # return the results
    if (simple) {

      return(summaryPerm$Pval)

    } else if (!simple) {

@@

``` {r 16.2.1. Overall Proportion/Earnings,fig.align="center",fig.width=10,fig.height=4, echo=FALSE}  
## ECDF of proportion completed per cost type
temp <- dataAll %>%
        filter(Choice < 2) %>%
        mutate(Cost = factor(Cost, levels = list("Physical", "Cognitive", "Wait", "Easy"))) %>%
        group_by(SubjID, Cost) %>%
        summarise(Earnings = sum(Reward[Choice == 1] / 100),
                  pComplete = mean(Choice))

## formal testing 
# proportion completed
propAov <- aov(pComplete ~ factor(Cost), data = temp)

propTests <- temp %>% 
  plyr::dlply("Cost", identity) %>%
  sapply("[[", "pComplete") %>%
  as.data.frame() %>%
  combn(2, simplify = F) %>%
  sapply(function(x) {
    c(contrast = paste(colnames(x), collapse = "vs"), 
      permPval = round(permute(x[, 1], x[, 2], simple = T), digits = 3),
      cohenD = round(cohenD(x[, 1], x[, 2]), digits = 3))
  }) %>% 
  t()

# pairwise.wilcox.test(temp$pComplete, temp$Cost)

# earnings
earnAov <- aov(Earnings ~ factor(Cost), data = temp)

earnTests <- temp %>% 
  plyr::dlply("Cost", identity) %>%
  sapply("[[", "Earnings") %>%
  as.data.frame() %>%
  combn(2, simplify = F) %>%
  sapply(function(x) {
    c(contrast = paste(colnames(x), collapse = "vs"), 
      permPval = round(permute(x[, 1], x[, 2], simple = T), digits = 3),
      cohenD = round(cohenD(x[, 1], x[, 2]), digits = 3))
  }) %>% 
  t()

# plots
p1 <- ggplot(aes(pComplete, color = Cost), data = temp) +
        stat_ecdf(lwd = 1.2, show.legend = F) +
        scale_color_manual(values = cols) +
        xlim(0, 1) +
        labs(y="ECDF", x = "Proportion Accepted") +
        theme(panel.grid.major = element_blank(), 
              panel.grid.minor = element_blank(), 
              panel.background = element_blank(), 
              axis.line = element_line(colour = "black"),
              text = element_text(size = 16))

p2 <- ggplot(temp, aes(Cost, pComplete, fill = Cost)) + 
        geom_boxplot(show.legend = F) +
        scale_fill_manual(values = cols) +
        ylim(c(0, 1)) +
        labs(y = "Proportion Completed") +
        theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(), 
            panel.background = element_blank(), 
            axis.line = element_line(colour = "black"),
            text = element_text(size = 16))

p3 <- ggplot(temp, aes(Cost, Earnings, fill = Cost)) + 
        geom_boxplot(show.legend = F) +
        scale_fill_manual(values = cols) +
        labs(y = "Total Earnings (dollars)") +
        theme(panel.grid.major = element_blank(), 
            panel.grid.minor = element_blank(), 
            panel.background = element_blank(), 
            axis.line = element_line(colour = "black"),
            text = element_text(size = 16))
